Bird beak's elaboration and innovation

### 2023-05-11 Analysis/05-Figure_with_phylogeny.Rmd
Update 05-Figure_with_phylogeny.Rmd

```{r, echo = FALSE}
library(ggtree)
library(ggtreeExtra)
library(treeio)
library(treeplyr)
library(ggplot2)
library(phytools)
library(motmot)
library(viridis)
library(RColorBrewer)
library(colorspace)
library(ggnewscale)

@@

# Set up data in long format with fudge to get variable names to plot correctly
heatmapdat <- beak[,c(1:3,5:8)]
colnames(heatmapdat) <- c("species", "Elaboration (all)", "Innovation (all)", 
                      "Elab (superorder)", "Innov (superorder)",
                      "Elab (order)", "Innov (order)")

>>>>

```{r, echo = FALSE}
library(ggtree)
library(ggtreeExtra)
library(treeio)
# install_github("uyedaj/treeplyr")
library(treeplyr)
library(dplyr)
library(ggplot2)
library(phytools)
library(motmot)
library(viridis)
library(RColorBrewer)
library(colorspace)
library(ggnewscale)

@@

# Set up data in long format with fudge to get variable names to plot correctly
heatmapdat <- beak[,c(1:3,5:8)]
colnames(heatmapdat) <- c("species", "Elaboration (all)", "Innovation (all)", 
                      "Elab (superorder)", "Innov (superorder)",
                      "Elab (order)", "Innov (order)")
## Just orders
heatmapdat <- beak[,c(1,7,8)]
colnames(heatmapdat) <- c("species", "Elaboration", "Innovation")
